\documentclass[12pt,a4paper]{article}
\usepackage{geometry}
\usepackage[numbers]{natbib}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{gensymb}
\usepackage[font=small]{caption}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage[raggedright]{titlesec}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{dirtytalk}
\usepackage{framed}
\usepackage[pdftex,breaklinks]{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = green, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = red %Colour of citations
}


\begin{document}
\author{Katrina Ashton}


\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{u5586882}

\section{What I've done}
\begin{itemize}
\item{Started assembling UAV (Frame done, most of the wiring done. Still need to attach gimbal, RealSense and TX2 and to set up the transmitter and receiver.)}
\item{Updated project propsal form after last week (see attached).}
\item{Started reading about ICP (just the surveys so far).}
\item{Started setting up TX1 (at home) -- will probably have to re-do this though as I'm currently using a vm.}
\end{itemize}

\section{Parts of report to look at}
\begin{itemize}
\item{Updated outline - can just have a look at the contents}
\item{Started introduction - 2 on page 2}
\item{Started lit review - 3.1 on page 2. Right now only results from the two surveys, so will need to add more papers. Will probably also have to add papers that were referenced in the surveys.}
\end{itemize}

\section{Questions}
\begin{itemize}
\item
\end{itemize}

\section{Comments}
\begin{itemize}
\item{Jean Luc says I need to either borrow a laptop or dual-boot mine. Haven't dual booted yet but I have a 73GB partition that I could probably use for that (Jean Luc said 50GB should be more than enough).}
\item{I have a gimbal, not mounted yet though.}
\item{Having some trouble setting up the reciever and controller.}
\item{Need to get project propsal form signed soon (due end of next week).}
\end{itemize}

\end{document}