\documentclass[12pt,a4paper]{article}
\usepackage{geometry}
\usepackage[numbers]{natbib}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{grffile}
\graphicspath{{../Figures/}}
\usepackage{gensymb}
\usepackage[font=small]{caption}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage[raggedright]{titlesec}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{dirtytalk}
\usepackage{framed}
\usepackage[pdftex,breaklinks]{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = green, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = red %Colour of citations
}


\begin{document}
\author{Katrina Ashton}


\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{u5586882}

\section{What I've done}
\begin{itemize}
\item{Finished and submitted mid term report.}
\item{Put new RealSense mount on quad.}
\item{Tried to fly quad with a longer period for the circles, but it crashed.}
\item{Started adding stuff from the mid-term report and these weekly summaries to the draft of my final report}
\item{Started filling in the appendices for my final report}
%\item{Added more to the appendices for the final report draft}
\end{itemize}

\section{Parts of report to look at}
\begin{itemize}
\item{New stuff is in blue. Sections 5 and 6 are new and I've added a bit here and there to previous sections. Section 5 has stuff from the mid-term report and last week's report. Section 6 mostly has stuff from previous weekly reports. }
\end{itemize}

\section{Questions}
\begin{itemize}
\item
\end{itemize}

\section{Comments}
\begin{itemize}
\item I tried flying the quad with a period of 60 seconds instead of 40 seconds for the circles. It crashed towards the end of the second circle both times I tried it. The battery was at about 3.8 per cell both times and it crashed in slightly different places, so I'm fairly sure that the issue was the battery running out rather than the Vicon dropping.
\item I tried another flight with a period of 50 seconds instead, but the tape that was holding the RealSense camera in place slipped. The quadcopter crashed and the blades shredded the cover of the RealSense camera.
\item Probably going to try another flight after our meeting, 50 seconds with reduced hover time.
\end{itemize}

\end{document}