\documentclass[12pt,a4paper]{article}
\usepackage{geometry}
\usepackage[numbers]{natbib}
\usepackage{amssymb, amsmath}
\usepackage{graphicx}
\usepackage{gensymb}
\usepackage[font=small]{caption}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage[raggedright]{titlesec}
\usepackage{subcaption}
\usepackage{multirow}
\usepackage{dirtytalk}
\usepackage{framed}
\usepackage[pdftex,breaklinks]{hyperref}
\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = green, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor   = red %Colour of citations
}


\begin{document}
\author{Katrina Ashton}


\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{u5586882}

\section{What I've done}
\begin{itemize}
\item{Downloaded toolchain for cross-compiling for the TX1}
\item{Got simple helloworld program cross-compiled for TX1}
\item{Started writing data capture code (modified from example code)}
\item{Attempted to build the data capture code but ran into a bunch of issues. Tried building the example code but couldn't get that working either.}
\item{Wrote draft feature list}
\end{itemize}

\section{Parts of report to look at}
\begin{itemize}
\item{Hasn't changed since last week}
\end{itemize}

\section{Questions}
\begin{itemize}
\item{}
\end{itemize}

\section{Comments}
\begin{itemize}
\item{Spent most of this week trying to wrap my head around cmakefiles/makefiles and librealsense. So unfortunately not too much tangible progress.}
\item{RealSense code won't even build on my laptop, let alone building bits of it. Seems like you need to use various install commands? Although I haven't found any of those that work properly either. (Got it installed on TX1 using jetsonhacks install scripts).}
\item{Also cannot build specific files on TX1.}
\item{I probably need to go through the cmake files for the RealSense code more carefully if I want to actually be able to build any of it.}
\item{Probably also need to read up a bit more on C/C++.}
\end{itemize}

\end{document}